Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
Minor changes

\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are bounded uncorrelated white noises.
% 
\end{myassumption}

>>>>

\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are uncorrelated white noises and their amplitudes are always bounded by the half of quantization step, {\it i.e.} $\vert \nu_{1} \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$, where $q_{1}$ and $q_{2}$ are respectively the quantization step of  ADC and DAC.
% 
\end{myassumption}
